Symbolic Weighted Language Models and\\ Quantitative Parsing over Infinite Alphabets

### 2021-10-11 algo-best-alt.tex
proof algo cont.

\begin{lemma}[Completeness]
For all $q_1, q_2 \in Q$, $p\in P$, 
($i$) there exists a path $\pi$ of $\G_A$ 
such that $\src(\pi) = \<q_0, q_0>$ for some $q_0 \in Q$, 
$\trg(\pi) = \< q_1, q_2>$,
and $\weight(\pi) = b_\bot(q_1, q_2)$, 
($ii$) there exists a path $\pi'$ of $\G_A$ 
such that $\src(\pi) = \<q_0, q_0>$ for some $q_0 \in Q$, 
$\trg(\pi) = \< q_1, p, q_2>$,
and $\weight(\pi) = b_\top(q_1, q_2)$.
\end{lemma}
%
\begin{proof}
By~\eqref{eq:bbot}, 
and since $\Semiring$ is total, for all $q_1, q_2 \in Q$, 
there exists one or several $t \in \Delta^*$ such that  
$b_\bot(q_1, q_2) = \weight_A\bigl(\config{q_1}{\bot}, t, \config{q_2}{\bot}\bigr)$.
Let $T(q_1, q_2) \subseteq \Delta^*$ denotes the set of such words $t$. % of minimal length.
%
Moreover, following~\eqref{eq:SWVPA-weight}, and by distributivity and commutativity in $\Semiring$, 
$b_\bot(q_1, q_2)$ is equal to a finite product $\bigotimes_{i=0}^n w_i(\tau_i)$, 
where every $\tau_i$ is a transition of $A$, every $w_i$ is one of the functions of $\bar\wei$,
the sequence of input symbols in $\tau_0,\ldots, \tau_n$ belongs to $T(q_1, q_2)$, 
$\src(\tau_0) = q_1$, and $\snd(\tau_n) = q_2$, where 
$\src(\tau)$ (resp. $\snd(\tau)$) is the first (resp. second) state component of a transition~$\tau$.
There may be several such sequences of $\tau_i$ and $w_i$, we choose an arbitrarily one of minimal length $n$.

%We represent a computation of $A$ on $t$ by a sequence $\rho$ of its transitions,

>>>>

\begin{lemma}[Completeness]
For all $q, q' \in Q$, $p\in P$, 
($i$) there exists a path~$\pi$ of~$\G_A$ 
such that $\src(\pi) = \<q_0, q_0>$ for some $q_0 \in Q$, 
$\trg(\pi) = \< q, q'>$,
and $\weight(\pi) = b_\bot(q, q')$, 
($ii$) there exists a path $\pi'$ of $\G_A$ 
such that $\src(\pi) = \<q_0, q_0>$ for some $q_0 \in Q$, 
$\trg(\pi) = \< q_1, p, q_2>$,
and $\weight(\pi) = \bigoplus_\Deltac b_\top(q_1, p, q_2)$.
\end{lemma}
%
\begin{proof}
By associativity, commutativity and distributivity for $\Semiring$,
\eqref{eq:bbot} can be rewritten into the form, unfolding~\eqref{eq:SWVPA-weight}:
\[
b_\bot(q, q') = 
\bigoplus_{t\in \Delta^*} 
\bigoplus_{\begin{array}{c}
           \scriptstyle q_0,\ldots, q_n \in Q\\
           \scriptstyle p_{i},\ldots, p_{k} \in P
           \end{array}}
\bigotimes_{i=i}^n w_i(\tau_i)           
\]
where $n$ is the length of $t$, $k \leq n$,
$q_0 = q$, $q_n = q'$, 
for all $1 \leq i < n$, 
$w_i$ is one of the functions of $\bar\wei$,
$\tau_i$ is a transition of $A$ and
$\src(\tau_i) = q_{i-1}$, $\snd(\tau_i) = q_i$.
%
Since $\Semiring$ is total, there exists finite sequences as above such that
\( b_\bot(q, q') = \bigotimes_{i=i}^n w_i(\tau_i)\).
%
There might exists, for $q$ and $q'$,
several finite sequences~$\bar\tau$ and~$\bar{w}$ as above, 
let us choose arbitrarily one of minimal length~$n$. 
This integer $n$ will be denoted $n_{q, q'}$ in the following.
%We represent a computation of $A$ on $t$ by a sequence $\rho$ of its transitions,

Similarly, following~\eqref{eq:btop} and~\eqref{eq:SWVPA-weight}, 
$\bigoplus_\Deltac b_\top(q_1, q_2)$ can be put in the form:
\[
{\textstyle\bigoplus_\Deltac} b_\top(q_1, q_2) = 
{\textstyle\bigoplus_\Deltac} \bigoplus_{t\in \Delta^*} 
\bigoplus_{\begin{array}{c}
           \scriptstyle q_0,\ldots, q_n \in Q\\
           \scriptstyle p_{i},\ldots, p_{k} \in P
           \end{array}}
\bigotimes_{i=i}^n w_i(\tau_i)           
\]
and hence 
\( {\textstyle\bigoplus_\Deltac} b_\top(q_1, q_2) = \bigotimes_{i=i}^n w_i(\tau_i) \),
using $c \in \Deltac$ that minimize...
We denote the smallest $n$ as above by $n_{q, p, q'}$.
